Learning Augmented Joint-Space Task-Oriented Dynamical Systems: \\ A Linear Parameter Varying and Synergetic Control Approach

### 2017-10-27 paper/main_RA-L_v1.tex
My comments and modifications.

\usepackage{blindtext}
\usepackage{graphicx}
\usepackage{url}
\usepackage[font={footnotesize}]{caption}
\usepackage[font={footnotesize}]{subcaption}
\usepackage[usenames, dvipsnames]{color}
\usepackage{amsmath}
\renewcommand{\labelenumii}{\Roman{enumii}} 
\usepackage{authblk}
\usepackage{hyperref}
% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
\usepackage{amssymb}

@@

\IEEEpeerreviewmaketitle
\section{Introduction}
\label{sec:intro}
Robot motion planning in joint-space has long been a major field of study \cite{kelly2006control}. For manipulation problems with an objective defined in task space (i.e. target or desired trajectory), we can often find a myriad of joint-space trajectories to achieve the same task-space goal. In many cases, however, certain joint-space trajectories are favored over others; for example, when we expect the robot to follow a desired joint-space behavior or ``style", as illustrated in Fig. \ref{fig:robot_example}.

@@

\begin{figure}[t]
\centering
\includegraphics[scale=.23,trim={0 0 0 0cm},clip]{Without_Obstcle_white_new.png}
\includegraphics[scale=.23,trim={0 0 0 0cm},clip]{With_Obstcle.png}
\caption{Two robot motions in \textcolor{orange}{\textbf{joint-space}} accomplishing \textit{similar} behavior in \textcolor{cyan}{\textbf{task-space}} (pouring chips in a bowl). The bottom example avoids a known obstacle in its workspace, while the top one does not.}
\label{fig:robot_example}
\vspace{-10pt}
\end{figure}

@@

Although DS-based task-space learning techniques ensure target convergence and stability, an advantageous feat within the LfD paradigm, they still suffer from this reliance on IK methods, possibly generating erratic or discontinuous motions during execution. Further, for certain tasks, rather than blindly choosing the arbitrary joint-space trajectory returned by the IKs solver, it might be desirable to learn behaviors and ``styles" in joint-space directly.  For example, throwing a ball is a motion less characterized by task-space behaviors (the ball moving backwards and then forwards) and more characterized by the joint behaviors: the elbow folds, the shoulder moves back and then swings forward, followed by the elbow straightening and the wrist snapping down. For a visual example of the need for such combined task/joint-space behavior learning, see Fig. \ref{fig:robot_example}. This is precisely the shortcoming associated with LfD in task-space: it fails to learn the joint-space behavior of the system. The current formulation of the DS-based learning techniques introduced thus far (e.g. SEDS, $\tau$-SEDS LMDS, etc.) do not allow for integrating combined task/joint-space behavior learning. \cite{calinon2008probabilistic} notably attempted to address this problem by learning separate motion policies in task space and the null space of the Jacobian (which would not affect task-space position), and driving the robot with a weighted sum of the two. However, this approach no longer guarantees convergence to the desired task-space target and is still reliant on computing the pseudo-inverse Jacobian.

%\cite{lee2014unifying} learns from demonstration in both joint and task space within the "thin-plate spline" trajectory warping framework, but does not propose a dynamical system for generating motions.

In this work, we seek to devise an augmented \textbf{J}oint-space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem (JT-DS) that not only incorporates task-space attractors, but also avoids the problems generated by pseudo-inverse approximations. \cite{hersch2008reaching} proposed an approach with similar properties to this desiderata, where two concurrent DS, one in task-space and one in joint-space, are modulated by enforcing kinematic coherence constraints to avoid singularities. The resulting DS avoids singularities through generalization of the pseudo-inverse approximations. However, because the two DS have their own unique attractors, the non-linear interaction between them imposed by the kinematic constraints does not ensure that the combined DS has a unique attractor. This gives rise to spurious attractors or cycles, and thus must be carefully tuned in order to avoid them. In this work, we depart from any modulation or combination of DS and instead propose a novel dynamical system which:

@@

The most similar approach to our proposed DS is the Jacobian transpose (JT) control \cite{wolovich1984computational} method. JT control is an inverse kinematics
method that yields a dynamical system in joint space $\dot{q} = f(q)$ which converges stably (in the sense of Lyapunov) over time to a desired end-effector position $x^*$, without the need for pseudo-inverse computations. It shares some of our approach's advantages: fast computation and provable task-space stability. However, despite some previous work designing velocity adjustments by hand \cite{Shi2016}, this is the first known work to employ a JT system to learn behaviors from demonstrations while obeying the robots kinematic constraints.

@@

%\begin{figure}[t]
%\centering
%\includegraphics[width=0.95\linewidth,trim={0 20 450 0},clip]{Pic/Schematic.jpg}
%\includegraphics[width=0.9\linewidth,trim={580 20 0 0},clip]{Pic/Schematic.jpg}
%\caption{ Standard control architecture using Cartesian dynamical systems (DS)\textbf{(top)}  and our proposed approach \textbf{(bottom)}.}
%\label{fig:schematic}
%\end{figure}

\section{Problem Statement} \label{Sec:Prob}
Consider a robotic system with $d$ task-space dimensions and $m$ degrees of freedom. We direct the system using a joint position or joint velocity controller, which can have joint position limits and a maximum joint velocity. We are further provided with a set of $N$ demonstrated joint-space trajectories $D=\{\{q_{t,n},\dot{q}_{t,n}\}_{t=1,\dots, T_n}\}_{n=1,\dots,N}$, where $T_n$ is the number of the sample points of the $n^{\text{th}}$ demonstration. We refer to the system's joint-space position as $q=\begin{bmatrix} q^1 & \dots & q^m
\end{bmatrix}^T \in \mathbb{R}^m$, and to its task-space position as $x\in \mathbb{R}^d$.\footnote{For sake of brevity and simplicity, the time index, $t$, is dropped throughout the paper. } The kinematics of the robot are assumed to be known, hence, the robot's forward kinematics is indicated by $x = H(q)$ and its Jacobian is $J(q) = \frac{dx}{dq}\in \mathbb{R}^{m\times d}$.\\
We wish to formulate a dynamical system $\dot{q} = f(q)$ which satisfies the following two criteria:
\renewcommand{\labelenumi}{(\Roman{enumi})}
\begin{enumerate}
\item The dynamical system must be Lyapunov stable\footnote{Unless otherwise specified, "stability" in this paper always refers to global Lyapunov stability. We make no claim to proving global asymptotic stability, which is in fact impossible to achieve in a joint-constrained kinematic system. For example, any finite-size manipulator will always have regions beyond its reach that it cannot converge to.} with respect to a fixed task-space target $x^*$. This can be expressed by ensuring that the following Lyapunov function
\begin{equation}
V(q) = (H(q) - x^*)^TP(H(q) - x^*) 
\label{eq:Lyp}
\end{equation}
is stable; i.e. $\dot{V}(q)\leq0 ~\forall q\in Q$ and $V(q)=0~ \forall q\in Q^*$. Where  $Q=\{q|q^i_{min} < q^i < q^i_{max},~\forall i\in \{1,\dots,d\}\}$ and $Q^*=\{q|H(q)=x^*\wedge q\in Q\}$. $P\in \mathbb{R}^{d\times d} $ is a symmetric and positive definite matrix. $V(.)$ can be thought of as a metric for the task-space distance-to-go.
\item The dynamical system should encapsulate the desired joint-space behaviors such that the following metric is minimized
\begin{equation}
\vspace{-5pt}
e_{total} = \frac{1}{NT_n}\sum_{n=1}^N\sum_{t=0}^{T_n} \left \| \dot{q}_{d; t,n} - f(q_{t,n}) \right \|
\label{eq:optim_error}
\end{equation}
  where $\dot{q}_d$ is the desired ``true" velocity, and $f(\cdot)$ is the motion generation policy.
\end{enumerate}

%Lastly, we wish to capture joint-space behaviors in our dynamical system.
We make two decisions by the choice of behavior error metric \eqref{eq:optim_error}. First, the metric implicitly suggests that behaviors are defined by expert motions of the behavior, and that fulfilling a behavior means moving similarly to the experts' motion. Second, the type of feature of the trajectory that is being minimized is important. If instead the error feature were joint position distance $\sum_i\left \| q_{d,i} - q_i \right \|$ where $q_d$ is a vector of demonstrated positions, then executing a "behavior" would imply mimicking position, but not velocity. Alternatively, if the error feature were joint velocity direction $\sum_i \left | \frac{\dot{q}_{d,i}}{\left \| \dot{q}_{d,i} \right \|} - \frac{\dot{q}_i}{\left \| \dot{q}_i \right \|} \right |$ mimicking a "behavior" would involve following the motion profile, but not the motion's speed (so for example a slap and a push would exhibit the same behavior). By choosing the combined direction and magnitude of the joint velocity as the error, we are choosing to mimic the magnitude and direction of the motion, which \cite{gielniak2010stylized} suggests is visually most similar to the human definition of "joint motion style".
\section{Augmented \textbf{J}oint-Space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem} \label{Sec:DS}
\label{sec:proposed_system}
We propose the following augmented Joint-space Task-oriented Dynamical System (JTDS) to achieve the two criteria presented in \ref{eq:Lyp} and \ref{eq:optim_error}.
\begin{equation}
\label{eq:ds}
\dot{q} = f(q) = -A(q)J^T(q)P(H(q) - x^*)
\end{equation}
where $P\in \mathbb{R}^{d\times d}$, and $A(q)\in \mathbb{R}^{m\times m}$ is constructed using the Linear Parameter Varying system paradigm \cite{emedi2016fixed,7439839}, where the overall $A(q)$ is a changing linear combination of constant  matrices, each of which encodes a local joint-space synergy. 
\begin{equation}
\label{eq:A_def}
A(q) = \sum_{k=1}^{K}\theta_k(q)A_k 
\end{equation}
where $A_k\in \mathbb{R}^{m\times m} $ are the different synergies and $\theta_k(q)\in \mathbb{R}^{1}~\forall k\in\{1,\dots,K\} $ are the scheduling parameters\footnote{The scheduling parameters can be a function of time $t$, the states of the
system $q $ or external signals $d(t)$, i.e. $\theta_k (t, q(t), d(t))$. In this paper, we only consider it as a function of the states of the system. It is noteworthy that the presented stability proof can easily be extended for $\theta_k (t, q(t), d(t))$.} modulating each local synergy through time as well as space. Based on \eqref{eq:ds}, one can utilize different synergies in different regions, and compose them to create a more complex multi-behavior motion.

@@

A central question becomes how to modulate the synergies in different regions to yield our desired behavior. First, we assume that our desired behavior can be efficiently described\footnote{Given some original space $A$ and some behavior policy $\pi_A(a)$ in $A$, we say that a latent mapping $\phi(\cdot)$ and latent space $B: \{b = \phi(a) | a \in A$\}$ "efficiently describe" $\pi_A$ if there exists some policy $\pi_B(b)$ in $B$ such that we can deterministically reconstruct $\pi_A(a)$ given $\pi_B(\phi(a))$} using some sub-manifold of the joint-space, called the \emph{synergy space}. We would like to define the robot's policy in synergy space such that in different regions of the space, we will utilize different synergies. We are thus left with three problems: finding an underlying synergy-space $Z$ in which the behavior can be accurately controlled (defined by a mapping $\phi: Q \rightarrow Z$), finding a policy for modulating the synergies in different regions of the synergy space (defined by $\theta_k(q)~\forall k\in\{1,\dots,K\}$), and finding parameters for the synergies themselves (defined by $A_k~\forall k\in\{1,\dots,K\}$). Our choice of parameters must also obey the constraints laid out in \eqref{eq:first_criteria_stability}. We propose the following 3-step procedure.

@@

\subsection{Embedding Joint Configurations in Synergy Space}

@@

\subsection{Discovering Local Synergy Regions}
Given the set of projected joint position trajectories $D=\{\{\phi(q_{t,n})\}_{t=1,\dots, T}\}_{n=1,\dots,N}$ where $\phi(q_{t,n})$ is the lower-dimensional embedding of $q_{t,n}$, $t$ is the time-step and $N$ is the number of demonstrations, we seek to learn a set of regions of distinct local synergies, each defined by their corresponding scheduling parameter $\theta_k(q) = \theta'_k(\phi(q))$. Moreover, we would like for our scheduling parameters $\theta'_k(\phi(q))$ to have the following properties: (i) $0 \prec \theta'_k(\phi(q))$ and (ii) $\sum_{k=1}^{K}\theta'_k(\phi(q)) = 1$.

@@

\section{Experimental Validation} \label{Sec:Exp}

@@

The learning algorithm presented in the previous section, \eqref{eq:opt}, was implemented in MATLAB. In order to solve the semidefinite convex optimization problem, the YALMIP framework \cite{lofberg2004yalmip} was used. In all the experiments, the optimization is initialized multiple times, and the best resulting run is used for performance analysis. The source code for learning (MATLAB) and execution (C++) of the Augmented Joint-Space Task-Oriented Dynamical System together with data generated in these experiments are available on-line: 
\centerline{\small \underline{\url{https://github.com/epfl-lasa/JT-DS-Learning}}}

\textcolor{red}{1. Introduce Datasets and metrics}\\

\textcolor{red}{2. Table with Evaluation of Learning Schemes for JTDS Models on Different Datasets  and discussion of results}

\newpage
\subsection{JT-DS Performance Evaluation}
The performance of the proposed framework was evaluated on a 7-DOF robot arm, the KUKA LWR 4+. The robot is controlled on the joint position level (linearly interpolating from joint velocities) at a rate of $ 500 $ Hz. The resultant joint angles are filtered by a critically damped filter to avoid high torques. Our empirical validation consists of three sections, each highlighting a different advantage of the proposed dynamical system: (i) moving in singular configurations, (ii) following desired behaviors in joint and task spaces simultaneously, and (iii) fast computation/convergence time.

>>>>

\usepackage{blindtext}
\usepackage{graphicx}
\usepackage{url}
\usepackage[font={footnotesize}]{caption}
\usepackage[font={footnotesize}]{subcaption}
\usepackage[usenames, dvipsnames]{color}
\usepackage{amsmath}
\renewcommand{\labelenumii}{\Roman{enumii}} 
\usepackage{authblk}
\usepackage[hidelinks]{hyperref}
% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
\usepackage{amssymb}

@@

\IEEEpeerreviewmaketitle
\section{Introduction}
\label{sec:intro}
\textcolor{red}{We'll remove the subsection headings later..\\ Some comments:\\- Change PbD to LfD everywhere}
\subsection{\textcolor{red}{Motivation for learning joint+task-space behaviors}}
\textcolor{red}{*See comments in tex*}
% % TO YO: OUTLINE FOR RE-WRITING THIS PART
%1. Start with motivation of LfD  
%2. Mention that we can learn behaviors in either joint or task space 
%3. briefly summarize the approaches in each without going into detail; i.e. probabilistic models, DS, etc 
%4. Motivate why we want to learn behaviors in joint+task space: 1 is because of the implications of IK as we already discuss, 2 to mimic joint trajectories.. here give your example of why we would want that and mention applications such as table tennis[1], grasping[2] and bi-manual coordination [3].
%
%[1] Y. Huang, D. B ̈uchler, O. Koc, B. Scholkopf and J. Peters, “Jointly
%learning trajectory generation and hitting point prediction in robot table
%tennis,” in Proc. IEEE International Conference on Humanoid Robots,
%2016, pp. 650-655.
%
%[2] S. Calinon and A. Billard, “Statistical learning by imitation of competing constraints in joint space and task space,” Advanced Robotics,vol. 23, pp. 2059-2076, 2009.
%
%[3] J. Silverio, S. Calinon, L. Rozo and D. G. Caldwell, “Learning competing constraints and task priorities from demonstrations of bimanual skills,” arXiv:1707.06791, 2017.

Robot motion planning in joint-space has long been a major field of study \cite{kelly2006control}. For manipulation problems with an objective defined in task space (i.e. target or desired trajectory), we can often find a myriad of joint-space trajectories to achieve the same task-space goal. In many cases, however, certain joint-space trajectories are favored over others; for example, when we expect the robot to follow a desired joint-space behavior or ``style", as illustrated in Fig. \ref{fig:robot_example}.

@@

\begin{figure}[t]
\centering
\includegraphics[scale=.23,trim={0 0 0 0cm},clip]{Without_Obstcle_white_new.png}
\includegraphics[scale=.23,trim={0 0 0 0cm},clip]{With_Obstcle.png}
\caption{Two robot motions in \textcolor{orange}{\textbf{joint-space}} accomplishing \textit{similar} behavior in \textcolor{cyan}{\textbf{task-space}} (pouring chips in a bowl). The bottom example avoids a known obstacle in its workspace, while the top one does not.}
\label{fig:robot_example}
\end{figure}

@@

Although DS-based task-space learning techniques ensure target convergence and stability, they still suffer from this reliance on IK methods, possibly generating erratic or discontinuous motions during execution. Further, for certain tasks, rather than generating arbitrary joint-space trajectory returned by the IKs solver, it might be desirable to learn behaviors and ``styles" in joint-space directly.  For example, throwing a ball is a motion less characterized by task-space behaviors (the ball moving backwards and then forwards) and more characterized by the joint behaviors: the elbow folds, the shoulder moves back and then swings forward, followed by the elbow straightening and the wrist snapping down. For a visual example of the need for such combined task/joint-space behavior learning, see Fig. \ref{fig:robot_example}. This is precisely the shortcoming associated with LfD in task-space: it fails to learn the joint-space behavior of the system. The current formulation of the DS-based learning techniques introduced thus far (e.g. SEDS, $\tau$-SEDS LMDS, etc.) do not allow for integrating combined task/joint-space behavior learning.

\subsection{\textcolor{red}{Approaches that tackle the joint+task problem}}
\textcolor{red}{*See comments in tex*}
% TO YO:
% ADD THESE THREE REFERENCES HERE AND SUMMARIZE THEM
%[1] Y. Huang, D. B ̈uchler, O. Koc, B. Scholkopf and J. Peters, “Jointly
%learning trajectory generation and hitting point prediction in robot table
%tennis,” in Proc. IEEE International Conference on Humanoid Robots,
%2016, pp. 650-655.
%
%[2] S. Calinon and A. Billard, “Statistical learning by imitation of competing constraints in joint space and task space,” Advanced Robotics,vol. 23, pp. 2059-2076, 2009.
%
%[3] J. Silverio, S. Calinon, L. Rozo and D. G. Caldwell, “Learning competing constraints and task priorities from demonstrations of bimanual skills,” arXiv:1707.06791, 2017.

\cite{calinon2008probabilistic} notably attempted to address this problem by learning separate motion policies in task space and the null space of the Jacobian (which would not affect task-space position), and driving the robot with a weighted sum of the two. However, this approach no longer guarantees convergence to the desired task-space target and is still reliant on computing the pseudo-inverse Jacobian.

\cite{lee2014unifying} learns from demonstration in both joint and task space within the "thin-plate spline" trajectory warping framework, but does not propose a dynamical system for generating motions.

\subsection{Our proposed Approach}
\textcolor{red}{Dynamical System, Why?\\Linear Parameter Varying, Why?\\Lower-Dimensional Manifold, Why?\\}
In this work, we seek to devise an augmented \textbf{J}oint-space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem (JT-DS) that not only incorporates task-space attractors, but also avoids the problems generated by pseudo-inverse approximations. \cite{hersch2008reaching} proposed an approach with similar properties to this desiderata, where two concurrent DS, one in task-space and one in joint-space, are modulated by enforcing kinematic coherence constraints to avoid singularities. The resulting DS avoids singularities through generalization of the pseudo-inverse approximations. However, because the two DS have their own unique attractors, the non-linear interaction between them imposed by the kinematic constraints does not ensure that the combined DS has a unique attractor. This gives rise to spurious attractors or cycles, and thus must be carefully tuned in order to avoid them. In this work, we depart from any modulation or combination of DS and instead propose a novel dynamical system which:

@@

The most similar approach to our proposed DS is the Jacobian transpose (JT) control \cite{wolovich1984computational} method. JT control is an inverse kinematics
method that yields a dynamical system in joint space $\dot{q} = f(q)$ which converges stably (in the sense of Lyapunov) over time to a desired end-effector position $x^*$, without the need for pseudo-inverse computations. It shares some of our approach's advantages: fast computation and provable task-space stability. However, despite some previous work designing velocity adjustments by hand \cite{Shi2016}, this is the first known work to employ a JT system to learn behaviors from demonstrations. 
%while obeying the robots kinematic constraints.

@@

%\begin{figure}[t]
%\centering
%\includegraphics[width=0.95\linewidth,trim={0 20 450 0},clip]{Pic/Schematic.jpg}
%\includegraphics[width=0.9\linewidth,trim={580 20 0 0},clip]{Pic/Schematic.jpg}
%\caption{ Standard control architecture using Cartesian dynamical systems (DS)\textbf{(top)}  and our proposed approach \textbf{(bottom)}.}
%\label{fig:schematic}
%\end{figure}
\section{Problem Statement} \label{Sec:Prob}
Consider a robotic system with $d$ task-space dimensions and $m$ degrees of freedom. We direct the system using a joint position or joint velocity controller, which can have joint position limits and a maximum joint velocity. We are further provided with a set of $N$ demonstrated joint-space trajectories $D=\{\{q_{t,n},\dot{q}_{t,n}\}_{t=1,\dots, T_n}\}_{n=1,\dots,N}$, where $T_n$ is the number of the sample points of the $n^{\text{th}}$ demonstration. We refer to the system's joint-space position as $q=\begin{bmatrix} q^1 & \dots & q^m
\end{bmatrix}^T \in \mathbb{R}^m$, and to its task-space position as $x\in \mathbb{R}^d$.\footnote{For sake of brevity and simplicity, the time index, $t$, is dropped throughout the paper. } The kinematics of the robot are assumed to be known, hence, the robot's forward kinematics is indicated by $x = H(q)$ and its Jacobian is $J(q) = \frac{dx}{dq}\in \mathbb{R}^{m\times d}$.\\
We wish to formulate a dynamical system $\dot{q} = f(q)$ which satisfies the following two criteria:
\renewcommand{\labelenumi}{(\Roman{enumi})}
\begin{enumerate}
\item The dynamical system must be Lyapunov stable\footnote{Unless otherwise specified, "stability" in this paper always refers to global Lyapunov stability. We make no claim to proving global asymptotic stability, which is in fact impossible to achieve in a joint-constrained kinematic system. For example, any finite-size manipulator will always have regions beyond its reach that it cannot converge to.} with respect to a fixed task-space target $x^*$. This can be expressed by ensuring that the following Lyapunov function
\begin{equation}
V(q) = (H(q) - x^*)^TP(H(q) - x^*) 
\label{eq:Lyp}
\end{equation}
is stable; i.e. $\dot{V}(q)\leq0 ~\forall q\in Q$ and $V(q)=0~ \forall q\in Q^*$. Where  $Q=\{q|q^i_{min} < q^i < q^i_{max},~\forall i\in \{1,\dots,d\}\}$ and $Q^*=\{q|H(q)=x^*\wedge q\in Q\}$. $P\in \mathbb{R}^{d\times d} $ is a symmetric and positive definite matrix. $V(.)$ can be thought of as a metric for the task-space distance-to-go.
\item The dynamical system should encapsulate the desired joint-space behaviors such that the following metric is minimized
\begin{equation}
\vspace{-5pt}
e_{total} = \frac{1}{NT_n}\sum_{n=1}^N\sum_{t=0}^{T_n} \left \| \dot{q}_{d; t,n} - f(q_{t,n}) \right \|
\label{eq:optim_error}
\end{equation}
  where $\dot{q}_d$ is the desired ``true" velocity, and $f(\cdot)$ is the motion generation policy.
\end{enumerate}

%Lastly, we wish to capture joint-space behaviors in our dynamical system.
We make two decisions by the choice of behavior error metric \eqref{eq:optim_error}. First, the metric implicitly suggests that behaviors are defined by expert motions of the behavior, and that fulfilling a behavior means moving similarly to the experts' motion. Second, the type of feature of the trajectory that is being minimized is important. If instead the error feature were joint position distance $\sum_i\left \| q_{d,i} - q_i \right \|$ where $q_d$ is a vector of demonstrated positions, then executing a "behavior" would imply mimicking position, but not velocity. Alternatively, if the error feature were joint velocity direction $\sum_i \left | \frac{\dot{q}_{d,i}}{\left \| \dot{q}_{d,i} \right \|} - \frac{\dot{q}_i}{\left \| \dot{q}_i \right \|} \right |$ mimicking a "behavior" would involve following the motion profile, but not the motion's speed (so for example a slap and a push would exhibit the same behavior). By choosing the combined direction and magnitude of the joint velocity as the error, we are choosing to mimic the magnitude and direction of the motion, which \cite{gielniak2010stylized} suggests is visually most similar to the human definition of "joint motion style".
\section{Augmented \textbf{J}oint-Space \textbf{T}ask-oriented \textbf{D}ynamical \textbf{S}ystem} \label{Sec:DS}
\label{sec:proposed_system}
\textcolor{red}{Change semi-definite to definite everywhere\\Change overall $A(q)$ to $\mathcal{A}(q)$\\ Introduce 'behavior synergies' here\\}
We propose the following augmented Joint-space Task-oriented Dynamical System (JTDS) to achieve the two criteria presented in \ref{eq:Lyp} and \ref{eq:optim_error}.
\begin{equation}
\label{eq:ds}
\dot{q} = f(q) = -A(q)J^T(q)P(H(q) - x^*)
\end{equation}
where $P\in \mathbb{R}^{d\times d}$, and $A(q)\in \mathbb{R}^{m\times m}$ is constructed using the Linear Parameter Varying system paradigm \cite{emedi2016fixed,7439839}, where the overall $A(q)$ is a changing linear combination of constant  matrices, each of which encodes a local joint-space synergy. 
\begin{equation}
\label{eq:A_def}
A(q) = \sum_{k=1}^{K}\theta_k(q)A_k 
\end{equation}
where $A_k\in \mathbb{R}^{m\times m} $ are the different synergies and $\theta_k(q)\in \mathbb{R}^{1}~\forall k\in\{1,\dots,K\} $ are the scheduling parameters\footnote{The scheduling parameters can be a function of time $t$, the states of the
system $q $ or external signals $d(t)$, i.e. $\theta_k (t, q(t), d(t))$. In this paper, we only consider it as a function of the states of the system. It is noteworthy that the presented stability proof can easily be extended for $\theta_k (t, q(t), d(t))$.} modulating each local synergy through time as well as space. Based on \eqref{eq:ds}, one can utilize different synergies in different regions, and compose them to create a more complex multi-behavior motion.

@@

A central question becomes how to modulate the synergies in different regions to yield our desired behavior. First, we assume that our desired behavior can be efficiently described\footnote{Given some original space $A$ and some behavior policy $\pi_A(a)$ in $A$, we say that a latent mapping $\phi(\cdot)$ and latent space $B: \{b = \phi(a) | a \in A\}$ "efficiently describe" $\pi_A$ if there exists some policy $\pi_B(b)$ in $B$ such that we can deterministically reconstruct $\pi_A(a)$ given $\pi_B(\phi(a))$} using some sub-manifold of the joint-space, called the \emph{synergy space}. We would like to define the robot's policy in synergy space such that in different regions of the space, we will utilize different synergies. We are thus left with three problems: finding an underlying synergy-space $Z$ in which the behavior can be accurately controlled (defined by a mapping $\phi: Q \rightarrow Z$), finding a policy for modulating the synergies in different regions of the synergy space (defined by $\theta_k(q)~\forall k\in\{1,\dots,K\}$), and finding parameters for the synergies themselves (defined by $A_k~\forall k\in\{1,\dots,K\}$). Our choice of parameters must also obey the constraints laid out in \eqref{eq:first_criteria_stability}. We propose the following 3-step procedure.

@@

\subsection{Embedding Joint Configurations in Lower-Dimensional Space}

@@

\subsection{Discovering Local Behavior Synergies}
Given the set of projected joint position trajectories $D=\{\{\phi(q_{t,n})\}_{t=1,\dots, T}\}_{n=1,\dots,N}$ where $\phi(q_{t,n})$ is the lower-dimensional embedding of $q_{t,n}$, $t$ is the time-step and $N$ is the number of demonstrations, we seek to learn a set of regions of distinct local synergies, each defined by their corresponding scheduling parameter $\theta_k(q) = \theta'_k(\phi(q))$. Moreover, we would like for our scheduling parameters $\theta'_k(\phi(q))$ to have the following properties: (i) $0 \prec \theta'_k(\phi(q))$ and (ii) $\sum_{k=1}^{K}\theta'_k(\phi(q)) = 1$.

@@

\newpage
\section{Experimental Validation} \label{Sec:Exp}

@@

The learning algorithm presented in the previous section, \eqref{eq:opt}, was implemented in MATLAB. In order to solve the semidefinite convex optimization problem, the YALMIP framework \cite{lofberg2004yalmip} was used. In all the experiments, the optimization is initialized multiple times, and the best resulting run is used for performance analysis. The source code for learning (MATLAB) and execution (C++) of the Augmented Joint-Space Task-Oriented Dynamical System together with data generated in these experiments are available on-line: \\
\footnotesize Learning:  \underline{\url{https://github.com/epfl-lasa/JT-DS-Learning}}\\
\footnotesize Execution:  \underline{\url{https://github.com/epfl-lasa/JT-DS-lib}}\\
\normalsize

\begin{table}[t]
\centering
\scriptsize
\caption{Datasets used to Evaluate JT-DS learning approach }
\label{tab:datasets}
\begin{tabular}{l|l|l}
\hline\hline
Task Behavior Dataset            & \# Demos & \# Samples (25Hz) \\ \hline
Backhand Stroke     & 11       & 1223                    \\
Forehand Stroke     & 10       & 1424                    \\
Pouring - Free      & 9        & 1032                    \\
Pouring - Obstacle  & 11       & 1232                    \\
Foot Swing          & 8        & 1058                    \\
Singularity Motions & 10       & 1467                 \\ \hline\hline
\end{tabular}
\end{table}

To evaluate the proposed JT-DS learning algorithm we collected demonstrations from 6 different tasks (see Table \ref{tab:datasets}) which require mimicking the demonstrated joint-space behavior while reaching for a single target in task space. These $M$ demonstrations consist of ($14$-D) time-series $\boldsymbol{\xi}^{(i)} = \{\xi_1^{(i)},\dots,\xi_T^{(i)}\}$ for $i= \{1,\dots,M\}$. The $14$ dimensions in $\xi_t = [q_t,\dot{q_t}]^T$ correspond to joints-space positions and velocities.

\textcolor{red}{2. Table with Evaluation of Learning Schemes for JTDS Models on Different Datasets and discussion of results}
\newpage
\subsection{JT-DS Performance Evaluation}
The performance of the proposed framework was evaluated on a 7-DOF robot arm, the KUKA LWR 4+. The robot is controlled on the joint position level (linearly interpolating from joint velocities) at a rate of $ 500 $ Hz. The resultant joint angles are filtered by a critically damped filter to avoid high torques. Our empirical validation consists of three sections, each highlighting a different advantage of the proposed dynamical system: (i) moving in singular configurations, (ii) following desired behaviors in joint and task spaces simultaneously, and (iii) fast computation/convergence time.
